# Reproducible research Week-2 : Peer Assessment 1

```{r, echo=FALSE, results='hide', warning=FALSE, message=FALSE}
library(ggplot2)
library(scales)
library(Hmisc)
```

## Loading and preprocessing the data

```{r, results='markup', warning=TRUE, message=TRUE}
data <- read.csv("activity.csv")
```

## What is mean total number of steps taken per day?

```{r}
step_Day <- tapply(data$steps, data$date, sum, na.rm=TRUE)
qplot(step_Day, xlab='total step per day', ylab='Frequency', binwidth=400)
```

```{r}
step_Mean <- mean(step_Day)
step_Median <- median(step_Day)
```
Mean: `r step_Mean`
, Median:  `r step_Median`

## What is the average daily activity pattern?

```{r}
average_step <- aggregate(x=list(mean_step=data$step), by=list(interval=data$interval), FUN=mean, na.rm=TRUE)
```

```{r}
ggplot(data=average_step, aes(x=interval, y=mean_step)) + geom_line() + xlab("The 5-minute interval") + ylab("average of step") 
```

```{r}
average_step[which.max(average_step$mean_step), ]
```

## Imputing missing values

```{r}
num_missingvalue <- length(which(is.na(data$steps)))
```
Number of missing value: `r num_missingvalue`

#### Create a new dataset
```{r}
data_impute <- data
data_impute$steps <- impute(data$steps, fun=mean)
```

```{r}
step_Dayimpute <- tapply(data_impute$steps, data_impute$date, sum)
qplot(step_Dayimpute, xlab='Total number of steps', ylab='Frequency', binwidth=400)
```

```{r}
step_MeanDayimpute <- mean(step_Dayimpute)
step_MedianDayimpute <- median(step_Dayimpute)
```
Mean_impute: `r step_MeanDayimpute`
, Median_impute:  `r step_MedianDayimpute`

## Are there differences in activity patterns between weekdays and weekends?

#### Create a new factor variable in the dataset
```{r}
data_impute$dateType <-  ifelse(as.POSIXlt(data_impute$date)$wday %in% c(0,6), 'weekend', 'weekday')
```

```{r}
averagedata_impute <- aggregate(steps ~ interval + dateType, data=data_impute, mean)
ggplot(averagedata_impute, aes(interval, steps)) + 
    geom_line() + 
    facet_grid(dateType ~ .) +
    xlab("5-minute interval") + 
    ylab("average number of steps taken, averaged across all weekday days or weekend days")

```







